Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-08 paper-kelompok/main.tex
add SCTP weight

\subsection{Weight and Size}
The dimension produced are 120 mm x 131 x 207 mm. 
Product dimensions are affected by the number of components used in the system and the optical configuration used. 
The sensor's location, diffraction grating, and light source mainly influence the product's height. 
The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of ​​the product base. 
In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.

>>>>

\subsection{Weight and Size}
Weight measurement is done by placing the product on a digital scale.
Fig. \ref{device_weight} shows that the product's weight is 0.832 kilograms.

\begin{figure}[htbp]
    \centerline{\includegraphics[angle=90,scale=0.12]{SCTP_weight.jpg}}
    \caption{Device's weight meeasurement}
    \label{device_weight}
    \end{figure}

The dimension produced are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
Product dimensions are affected by the number of components used in the system and the optical configuration used. 
The sensor's location, diffraction grating, and light source mainly influence the product's height. 
The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of ​​the product base. 
In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.
